Wireless Automobile Detection, License Plate Processing, and Data Availability Network Proposal

### 2014-03-09 proposal/proposal.tex

Our goal is to work with the ACMx group to deploy the system in two parking lots on campus, the CTLM upper lot and CTLM lower lot, which are the two closest parking lots to the CTLM building on the Mines campus. The system itself will consist of five main subsystems, which are described in detail in section 2.

@@

\begin{thebibliography}{99}
\bibitem{stillwell2013} R. Stillwell, A. Wilson ``Magnetometer Parking Sensor'' \emph{EGGN 383 Final Project, Colorado School of Mines}. December 12, 2013

\bibitem{parkingWiki}  ACMx ``Parking Sensor Wiki'' \begin{verbatim}https://github.com/ColoradoSchoolOfMines/parking_sensor/wiki\end{verbatim} % Not sure how to cite this; can someone help?

>>>>

The goal of this project is to work with the ACMx group to deploy the system in two parking lots on campus, the CTLM upper lot and CTLM lower lot, which are the two closest parking lots to the CTLM building on the Mines campus. The system itself will consist of five main subsystems, which are described in detail in section 2.

@@

\begin{thebibliography}{99}
\bibitem{stillwell2013} R. Stillwell, A. Wilson ``Magnetometer Parking Sensor'' \emph{EGGN 383 Final Project, Colorado School of Mines}. December 12, 2013.

\bibitem{parkingWiki}  R. Stillwell ``Parking Sensor Wiki'' \url{http://github.com/ColoradoSchoolOfMines/parking_sensor/wiki}. % Not sure how to cite this; can someone help?
